---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# networkdata

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/networkdata)](https://cran.r-project.org/package=networkdata)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Downloads](https://cranlogs.r-pkg.org/badges/networkdata)](https://CRAN.R-project.org/package=networkdata)
<!-- badges: end -->

The package contains a large variety of different network datasets (all in `igraph` format). So far, it includes datsets from the following repositories: 

- Freeman's datasets from http://moreno.ss.uci.edu/data
- Movie networks from https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/T4HBA3
- Covert networks from https://sites.google.com/site/ucinetsoftware/datasets/covert-networks
- Animal networks from https://bansallab.github.io/asnr/
- Shakespeare's plays networks build with data from https://github.com/mallaham/Shakespeare-Plays

A list of all datasets can be obtained with
```{r data,eval=FALSE}
data(package = "networkdata")
```

So far, the package contains `r length(list.files("data"))` datasets. 

**Feel free to add your own datset via a pull request**

## Installation

You can install the developers version of networkdata with:

```{r install, eval=FALSE}
#install.packages("remotes")
remotes::install_github("networkdata")
```
